Pillar 1 - Sequential Pattern Mining

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
minor editing

  # Confidence and Lift
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  mutate(
    rhs.take = str_detect(rhs, "fail|pass")
    ) %>%
  group_by(
    lhs, rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support * rhs.take),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / (rhs.support + 1e-4) # some courses have a failure rate of 0%.
    ) %>%
  ungroup %>%

>>>>

  # Confidence and Lift
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  mutate(
    rhs.take = str_detect(rhs, "fail|pass")
    ) %>%
  group_by(
    lhs, rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support * rhs.take),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / (rhs.support + 1e-4) # increase denominator by smal value to avoid dividing by 0.
    ) %>%
  ungroup %>%
